% ══════════════════════════════════════════════════════════════════════
% Appendix A  Mixed-rank SU-SU no-Veneziano classes
% ══════════════════════════════════════════════════════════════════════

In the main text we focused on the equal-rank case
$\SU(N)_{1}\times\SU(N)_{2}$ with rank multipliers $(m_{1},m_{2})=(1,1)$.
The same classification pipeline applies at general coprime rank
multipliers and produces additional non-Veneziano universality classes
for
\begin{equation}
  G\;=\;\SU(m_{1}N)_{1}\times\SU(m_{2}N)_{2},
  \qquad\gcd(m_{1},m_{2})=1\,,
\end{equation}
with $(m_{1},m_{2})$ chosen up to a swap of the two nodes.  We retain
only classes with $m_{1},m_{2}\le 4$.

\paragraph{Inventory.}  Table~\ref{tab:mixed-rank-inventory} lists the
$20$ mixed-rank non-Veneziano classes with $a/N^{2}$ defined.  As in
the equal-rank case, every class satisfies $a=c$ to leading order in
$1/N$.

\begin{table}[h]
  \centering
  \small
  \begin{tabular}{cccrl}
    \toprule
    Class & $m_{1}$ & $m_{2}$ & \# theories & $a/N^{2}$ \\
    \midrule
    $111$ & $2$ & $1$ & $2$  & $-0.6328$ \\
    $117$ & $2$ & $1$ & $2$  & $0$         \\
    $121$ & $2$ & $1$ & $8$  & $0.7910$ \\
    $122$ & $2$ & $1$ & $8$  & $0.7922$ \\
    $134$ & $2$ & $1$ & $8$  & $1.0547$ \\
    $136$ & $2$ & $1$ & $16$ & $1.0760$ \\
    $153$ & $2$ & $1$ & $20$ & $1.1470$ \\
    $159$ & $2$ & $1$ & $3$  & $1.1897$ \\
    $160$ & $2$ & $1$ & $40$ & $1.1926$ \\
    $174$ & $2$ & $1$ & $6$  & $1.25$    \\
    $283$ & $3$ & $1$ & $8$  & $0.9722$ \\
    $298$ & $3$ & $1$ & $20$ & $2.3056$ \\
    $377$ & $3$ & $2$ & $8$  & $2.2222$ \\
    $384$ & $3$ & $2$ & $34$ & $2.4668$ \\
    $398$ & $3$ & $2$ & $20$ & $2.5477$ \\
    $437$ & $3$ & $2$ & $12$ & $2.9722$ \\
    $450$ & $3$ & $2$ & $88$ & $3.1192$ \\
    $681$ & $4$ & $3$ & $34$ & $4.9951$ \\
    $730$ & $4$ & $3$ & $12$ & $5.9425$ \\
    $731$ & $4$ & $3$ & $88$ & $5.9568$ \\
    \bottomrule
  \end{tabular}
  \caption{Mixed-rank non-Veneziano $\SU(m_{1}N)\times\SU(m_{2}N)$
    universality classes with $m_{1}\ne m_{2}$ (or $m_{1}=m_{2}>1$).
    $a/N^{2}$ is quoted to four decimal places; exact forms are
    available in the accompanying database.  All classes satisfy
    $a/c=1$ to leading order in $1/N$.}
  \label{tab:mixed-rank-inventory}
\end{table}

\paragraph{RG phase distribution.}  Running the boundary analysis of
Section~\ref{sec:boundary} on each mixed-rank class reveals the same
three topology types as in the equal-rank sector.  As in
Section~\ref{sec:boundary-phases}, none of the non-Veneziano
mixed-rank classes realise the Figure~6 topology at $\Nf=0$.
Single-parameter deformations analogous to the class-$16$ deformation
of Section~\ref{sec:phases-class16} can push individual classes into
the Figure~6 window; characterising which mixed-rank classes admit a
Figure~6 phase is a straightforward but tedious exercise we leave
for future work.

\paragraph{Class 117.}  Class 117 has $a/N^{2}=0$ at leading order,
analogous to the equal-rank class 1: the $a$-max lands on the boundary
$R_{\text{bif}}=0$ of the polytope and the theory is non-interacting
at leading $N$.

\paragraph{Negative $a/N^{2}$.}  Class $111$ returns a negative value
for the leading-$N$ $a$-maximum, which violates the expected
positivity of $a$ for a unitary SCFT.  The negative value signals
that the critical point is not in the physical R-symmetry polytope at
this order; the theory is either non-unitary or requires
subleading corrections for a physical characterisation.  We flag this
class as a cautionary boundary case rather than including it in the
topology-classification tables.
